---
title: "Situation Report"
author: "HZI Analysis, Output and Research"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  bookdown::word_document2:
    reference_docx: data/text/template.docx
    number_sections: true
    fig_width: 7
    fig_height: 6
    fig_caption: yes
bibliography: data/text/references.bib
link-citations: yes
---

```{r setup, include = FALSE}
# setting knitr chunk options
knitr::opts_chunk$set(echo = FALSE, tab.cap.style = "Table Caption")
```

```{r sitrep_data_setup, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
base::source(file.path(".", "global.R"))
```


```{r flextable settings, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
# In this SitRep the package 'flextable' is used to display tables in word.
# Here we set the default options for the flextable package.
# The flextable package automatically splits long tables over different pages 
# and repeats the headings.

set_flextable_defaults(big.mark = " ",
  font.size = 9, theme_fun = theme_vanilla,
  padding.bottom = 6,
  padding.top = 6,
  padding.left = 5,
  padding.right = 5,
  background.color = "#EFEFEF")

```

# Introduction
`r text["INTRO.docx",1]` 

## Overview
`r text["OVERVIEW.docx",1]`

```{r}
DisplayOverviewEpidTable()
```

# Epidemic Dynamic
`r text["EPID_DYN.docx",1]` 

## Time series data
`r text["TIME_SER.docx",1]`

PLOT TIMESERIES DATA

## Death incidences by age groups
`r text["DEATH_INC.docx",1]`

PLOT AGEGROUP GENDER DATA

# Regional Situation
`r text["REG_SIT.docx",1]`

## Region level table
`r text["STATE_TBL.docx",1]`

```{r}
DisplayRegionEpidTable()
```


## District level map
`r text["COUNTY_MAP.docx",1]`

DISPLAY DISTRICT LEVEL MAP

# Remarks 
`r text["REMARKS.docx",1]`

# References
```{r references, echo = FALSE, warning=FALSE, message=FALSE}
# References to papers can be included via the references.bib and the .docx
# files in the /text folder.
# First, the user needs to copy the BibTex reference of the paper he or she 
# wants to cite in the references.bib file. 
# Then, to define the place of the refence within the text, the user simply 
# needs to put '[@refname]' in the text of the .docx file where the citation
# should be. 
# To cite multiple references at once: '[@refname1;@refname2]'.
# refname is the BibTex reference name of the paper to be cited.

# For crossreferences to section headings the user needs to type 
# 'Section \@ref(label)' in the text witin the .docx file in the /text
# folder.
# 'label' is the Section ID of the section to be cited, which is defined by
# through Pandoc as e.g. 'heading-one' for a Section named '# Heading one'.
# The user can define section IDs by adding '{#userdefinedID}' behind a
# heading, e.g. '# Heading {#userdefinedID}'.

# For crossreferences to figures the user needs to type 
# 'Figure \@ref(fig:FigName)' in the text witin the .docx file in the /text
# folder.
# FigName is the name of the figure to be cited, which is defined in the chunk
# options of this Situation-Report.Rmd file.

# For crossreferences to tables the user needs to type 
# 'Table \@ref(tab:TabName)' in the text witin the .docx file in the /text
# folder.
# TabName is the name of the table to be cited, which is defined in the chunk
# options of this Situation-Report.Rmd file.

```